Poincar\'e--Friedrichs constants over triangulated domains

### 2024-06-15 main.tex
more theory

\documentclass[a4paper]{amsart}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\input{header}

@@

Given any simplex $T$, we write $\subsimplex(T)$ for the simplicial complex that contains all subsimplices of $T$. 
More specifically, $\subsimplex_{{k}}(T) \subseteq \subsimplex(T)$ denotes the set of $k$-dimensional subsimplices of $T$. 
Whenever $\calT$ is a simplicial complex and $T \in \calT$, we let $\supsimplex(\calT,T)$ be the set of simplices in $\calT$ that contain $T$.
We write $\supsimplex_{k}(\calT,T)$ for the set of $k$-dimensional simplices in $\supsimplex(\calT,T)$. 
Additionally, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Edges(\calT) := \subsimplex_{1}(\calT)$ refer to the vertices and edges of the simplicial complex, respectively. Similarly, if $\calT$ is an $n$-dimensional simplicial complex, we write $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ for the faces (codimension $1$ members) of this triangulation.

@@

We return to the theory of triangulations,
as our main objective requires some further concepts.
We are interested in simplicial complexes that triangulated manifolds. 
We put particular focus on \emph{shellable} simplicial complexes as a particularly important class of complexes. Such simplicial complexes are constructed by successively adding simplices in a particularly well-behaved manner. Patches within triangulations are examples of such shellable complexes. 
Our main references for this section are the monographs by Kozlov~\cite{kozlov2008combinatorial} and Ziegler~\cite{ziegler2012lectures}. 
\\

@@

We define an $n$-dimensional simplicial complex to be a \emph{manifold triangulation} if the underlying set $\underlying{\calT}$ is an $n$-dimensional manifold with boundary.
We recall that this means that for every $x \in \underlying{\calT}$
there exists $\epsilon > 0$ and an embedding $\phi : \Ball_\epsilon(x) \cap \underlying{\calT} \rightarrow \bbR^n$
such that $\phi(0) = 0$ and $\phi$ is an isomorphism either onto the closed unit ball $\calB = \{ x \in \bbR^n \suchthat |x| \leq 1 \}$
or onto $\{ x \in \calB \suchthat x_1 \geq 0 \}$.
Any simplicial complex that triangulates an $n$-dimensional manifold must be an $n$-dimensional simplicial complex.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% TODO: integrate into narrative 
Those simplices of the manifold triangulation that are subsets of the boundary of the underlying manifold are called \emph{boundary simplices}. 
All other simplices of the manifold triangulation are called \emph{inner simplices}. 
We will show soon that the boundary simplices of a manifold triangulation constitute a triangulation of the manifolds boundary. 
% 
%
Suppose that $\calT$ is an $n$-dimensional manifold triangulation. 
The simplices that lie in the boundary of the underlying set are called \emph{boundary simplices}.
If $S$ lies in the boundary of the underlying set, then it lies within some boundary face.
and so we conclude that the family of boundary faces constitute a simplicial complex, which we call \textit{boundary complex}.
Any point on the boundary lies within some boundary simplex, and hence the boundary complex is a triangulation of the boundary. 
Definitions imply that the boundary complex is a manifold triangulation of dimension $n-1$.
% 
%
The boundary simplices of a manifold triangulation of dimension $n$ constitute a manifold triangulation themselves, of dimension $n-1$, which triangulate the boundary of the underlying space. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We gather a few helpful properties of manifold triangulations. 
While the reader might deem them obvious, we nevertheless include proofs.

\begin{lemma}\label{lemma:characterizationofmanifoldcomplexes}
    Let $\calT$ be a finite $n$-dimensional simplicial complex whose underlying space is a manifold $\calM$. 
    \begin{itemize}
        \item Any face $F \in \Faces(\calT)$ is not contained in the boundary if and only if it is contained in exactly two $n$-simplices.
        \item Any face $F \in \Faces(\calT)$ is contained in the boundary if and only if it is contained in exactly one $n$-simplex.
        \item The simplices contained in the boundary constitute a triangulation of the boundary.
        % \item $\calT$ is non-branching, that is, every $F \in \calT$ of dimension $n-1$ is contained in at most two $n$-simplices of $\calT$. 
        \item If $S$ is an inner simplex, then $\patch_{\calT}(S)$ is a simplicial $n$-ball with $S$ as an inner simplex
        and $\carapace_{\calT}(S)$ is a simplicial $(n-1)$-sphere. 
        \item If $S$ is a boundary subsimplex, then $\patch_{\calT}(S)$ is a simplicial $n$-ball with $S$ as a boundary simplex,
        and $\carapace_{\calT}(S)$ is a simplicial $(n-1)$-ball.
        \item If the underlying space of $\calT$ is connected, then $\calT$ is strongly connected.
    \end{itemize}
\end{lemma}
\begin{proof}
    \begin{enumerate}
    \item 
    We $\mathring \calM := \calM \setminus \partial \calM$ denote the interior of the manifold. 
    We will use the following fact: if $S \in \calT$ has an inner point that lies on $\partial \calM$, then all inner points of $S$ are on $\partial \calM$. 
    Since the boundary is closed, every $S \in \calT$ is either a subset of the boundary or all its inner points lie in the interior $\mathring \calM$ of the manifold.

@@

    \item
    Clearly, the simplices of $\calT$ contained in the boundary constitute a simplicial complex. 
    If $x \in \partial \calM$ is a boundary simplex, then it is an inner point of some simplex $S \in \calT$.
    But then this simplex must be a boundary simplex, so the boundary simplices form a triangulation of $\partial \calM$.

    \item 
    Let $S$ be any simplex with vertices $v_0, v_1, \dots, v_k$, with midpoint $z_F$, and dimension $k$.
    Let $\calS := \patch_{\calT}(S)$ be its star. 
    Each $l$-dimensional simplex $T \in \calS$ that contains $S$ 
    has vertices $v_0, v_1, \dots, v_k, v_{k+1}^{S}, \dots, v_{l}^{S}$. 
    For any such simplex, we introduce a decomposition $T_{0}, \dots, T_{k}$, where each $T_{i}$ has vertices 
    \begin{align*}
        v_0, \dots, v_{i-1}, z_F, v_{i+1}, \dots, v_k, v_{k+1}^{S}, \dots, v_{l}^{S}.
    \end{align*}
    The collection $\calS'$ of these simplices and their subsimplices constitute a simplicial complex 
    that triangulates the same underlying set as $\calS$.
    Moreover, $\calS' = \patch_{\calS'}(z_F)$. 
    In particular, $z_F$ is a boundary vertex of $\calS'$ if and only if $S$ is a boundary simplex of $\calS$.

    So it remains to study the topology of vertex stars. Suppose that $S = \{z\}$ is a singleton simplex. 
    For $\delta > 0$ small enough, 
    \begin{align*}
        B_{\delta}(z) = \left\{ x \in M \suchthat d(x,z) \leq \delta \right\},
        \quad 
        S_{\delta}(z) = \left\{ x \in M \suchthat d(x,z) = \delta \right\},
    \end{align*}
    are subsets of $\patch_{\calT}(S)$.
    For each $K \in \patch_{\calT}(S)$ that contains $S$ and which has the complementary simplex $F_S$, 
    we easily find homeomorphisms $\phi_{K} : B_{\delta}(z) \cap K \rightarrow K$
    such that 
    $\phi_{K|S}$ is the identity,
    such that 
    $\phi_{K}(S_F) = S_{\delta}(z)$,
    and such that 
    for all $K, K' \in \calT$ with $K' \subseteq K$ we have $\phi_{K|K'} = \phi_{K'}$.

    If $z$ is an inner vertex of $\calS'$, 
    then the boundary simplices of $\calS'$,
    which are the boundary simplices of $\calS$, triangulate a topological sphere of dimension $n-1$.
    If $z$ is a boundary vertex of $\calS'$,
    which is the case if and only if $S$ is a boundary simplex, 
    then the underlying space of $\carapace(S)$ is homeomorphic to $S_{\delta}(z)$, 
    which is a topological ball of dimension $n-1$.

@@

Suppose that $\calT$ is an $n$-dimensional simplicial complex and we have an enumeration of the $n$-simplices $T_{0}, T_{1}, T_{2}, \dots \in \subsimplex_{n}(\calT)$.
For any enumeration, we call 
\[
    I_m 
    := 
    \big( \patch_{\calT}(T_{0}) \cup \patch_{\calT}(T_{1}) \cup \dots \cup \patch_{\calT}(T_{m}) \big) 
    \cap 
    \patch_{\calT}(T_{m+1})
\]
be the $m$-th \textit{interface complex}. Note that this intersection is automatically a subcomplex of the boundary complex of the last simplex $T_{m}$.
We call the enumeration a \emph{shelling} if each interface $I_m$ is a simplicial complex of dimension $n-1$.

\begin{remark}
    We interpret a shelling as the construction of a triangulation 
    by successively attaching simplices such that the intermediate triangulations are well-behaved. 
    Conversely, the reverse enumeration describes a successive decomposition of the triangulation, hence the name ``shelling''.
\end{remark}

\begin{example}
    Any simplex $T$ trivially has a shelling. The boundary complex $\partial \calT(T)$ has a shelling:
    in fact, any enumeration of the boundary faces of $T$ constitutes a shelling.
\end{example}
\begin{example}
    The standard triangulation of the $n$-dimensional cube, the Kuhn triangulation, is shellable. 
\end{example}
\begin{example}
    Not all trianguable sets admit a triangulation that is also shellable. 
    Moreover, even if a set admits a shellable triangulation, not all of its triangulations might be shellable. 
    We refer to~\cite[Example 8.9]{ziegler2012lectures} for an examples of non-shellable triangulations of cubes and tetrahedra in three dimensions. 
\end{example}

Our main interest are the local patches or stars within triangulations. 
It turns out that those are shellable.

\begin{lemma}    
    If an $n$-dimensional simplicial complex $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots$ and is non-branching, then it triangulates a manifold, possibly with boundary.
    In particular, $\patch_{\calT}(T_{0}) \cup \patch_{\calT}(T_{1}) \cup \dots \cup \patch_{\calT}(T_{m})$ triangulates a manifold for all $m \geq 0$.
\end{lemma}
\begin{proof}    
\end{proof}

The notion of shelling is taken from Ziegler's book~\cite{ziegler2012lectures}
\begin{lemma}    
    Any simplicial $2$-disk is shellable.
    Any simplicial $2$-sphere is shellable. 
\end{lemma}
\begin{proof}
    Let $\calT$ be a simplicial $2$-disk. 
    If $\calT$ contains only one triangle, then there is nothing to show. 
    Otherwise, there exists at least one triangle $T$ that touches the boundary of the disk at either one or two edges {\color{red}Needs proof}. 
    Letting $\calT'$ be the triangulation obtained by removing $T$,
    we have another triangulation of the $2$-disk that intersects $T$ only at either two or one edges.
    Repeating this procedure yields an enumeration of the triangles of $\calT$,
    whose reverse is a shelling.

@@

\begin{remark}
    Patches around boundary simplices are not necessarily shellable when the dimension exceeds $3$.
    For example, there exists a non-shellable triangulation of a tetrahedron. 
    If we extend this triangulation to a triangulation of a hypertetrahedron by suspending it from a new point $v_\star$, 
    then the resulting new triangulation is non-shellable and coincides with the patch around $v_\star$.
\end{remark}

@@

\begin{remark}
    Whether a simplicial complex is shellable can be checked, in principle, simply by trying out all the possibly enumerations.
    That we cannot do much better than this is captured in the result that testing for shellability is NP-complete~\cite{goaoc2019shellability}:
    this complexity result is even true if we merely consider simplicial complexes of dimension two embedded in some Euclidean space.
\end{remark}

@@

% Square 
% L-shaped 
% Slit
% Cube 
% Fechera
% Crossed bricks

>>>>

\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\input{header}

@@

Given any simplex $T$, we write $\subsimplex(T)$ for the simplicial complex that contains all subsimplices of $T$. 
More specifically, $\subsimplex_{{k}}(T) \subseteq \subsimplex(T)$ denotes the set of $k$-dimensional subsimplices of $T$. 
Whenever $\calT$ is a simplicial complex and $T \in \calT$, we let $\supsimplex(\calT,T)$ be the set of simplices in $\calT$ that contain $T$.
We write $\supsimplex_{k}(\calT,T)$ for the set of $k$-dimensional simplices in $\supsimplex(\calT,T)$. 
Additionally, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Edges(\calT) := \subsimplex_{1}(\calT)$ refer to the vertices and edges of the simplicial complex, respectively. 
In practice, we not always distinguish between points and singleton simplices. % TODO: see whether being formally correct iis possible 
Similarly, if $\calT$ is an $n$-dimensional simplicial complex, we write $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ for the faces (codimension $1$ members) of this triangulation.

@@

We return to the theory of triangulations,
as our main objective requires some further concepts.
We are interested in simplicial complexes that triangulated manifolds. 
We put particular focus on \emph{shellable} simplicial complexes as a particularly important class of complexes. Such simplicial complexes are constructed by successively adding simplices in a particularly well-behaved manner. Patches within triangulations are examples of such shellable complexes. 
Our main references for this section are the monographs by Kozlov~\cite{kozlov2008combinatorial} and Ziegler~\cite{ziegler2012lectures}.

@@

We define an $n$-dimensional simplicial complex to be a \emph{manifold triangulation} if the underlying set $\underlying{\calT}$ is an $n$-dimensional manifold with boundary.
We recall that this means that for every $x \in \underlying{\calT}$
there exists $\epsilon > 0$ and an embedding $\phi : \Ball_\epsilon(x) \cap \underlying{\calT} \rightarrow \bbR^n$
such that $\phi(0) = 0$ and $\phi$ is an isomorphism either onto the closed unit ball $\calB = \{ x \in \bbR^n \suchthat |x| \leq 1 \}$
or onto $\{ x \in \calB \suchthat x_1 \geq 0 \}$.
Any simplicial complex that triangulates an $n$-dimensional manifold must be $n$-dimensional.

We know that any manifold $\calM$ has a got a topological boundary $\partial\calM$, possibly empty. 
If $\calM$ is $n$-dimensional, then the $\partial\calM$ is a topological manifold without boundary of dimension $n-1$.

@@

We gather a few helpful properties of manifold triangulations. 
While the reader might deem them obvious, we nevertheless include proofs. 
We begin with the boundary.

\begin{lemma}\label{lemma:boundarysimplices}
    Let $\calT$ be a finite $n$-dimensional simplicial complex whose underlying space is a manifold $\calM$. 
    \begin{itemize}
        \item Any face $F \in \Faces(\calT)$ is not contained in the boundary if and only if it is contained in exactly two $n$-simplices.
        \item Any face $F \in \Faces(\calT)$ is contained in the boundary if and only if it is contained in exactly one $n$-simplex.
        \item The simplices contained in the boundary constitute a triangulation of the boundary.
        % \item $\calT$ is non-branching, that is, every $F \in \calT$ of dimension $n-1$ is contained in at most two $n$-simplices of $\calT$. 
    \end{itemize}
\end{lemma}
\begin{proof}
    We prove these statements in several steps.
    \begin{enumerate}
    \item 
    We $\mathring \calM := \calM \setminus \partial \calM$ denote the interior of the manifold. 
    We will use the following fact: if $S \in \calT$ has an inner point that lies on $\partial \calM$, then all inner points of $S$ are on $\partial \calM$. 
    Since the boundary is closed, every $S \in \calT$ is either a subset of the boundary or all its inner points lie in the interior $\mathring \calM$ of the manifold.

@@

    \item
    Clearly, the simplices of $\calT$ contained in the boundary constitute a simplicial complex. 
    If $x \in \partial \calM$ is a boundary simplex, then it is an inner point of some simplex $S \in \calT$.
    But then this simplex must be a boundary simplex, so the boundary simplices form a triangulation of $\partial \calM$.
    \end{enumerate}
    All relevant results are proven. 
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% TODO: integrate into narrative 
Suppose that $\calT$ is an $n$-dimensional simplicial complex that triangulates a manifold. 
Those simplices of the manifold triangulation that are subsets of the boundary of the underlying manifold are called \emph{boundary simplices}. 
% The simplices that lie in the boundary of the underlying set are called \emph{boundary simplices}.
All other simplices of the manifold triangulation are called \emph{inner simplices}.

We have seen that the boundary simplices of a manifold triangulation constitute a triangulation of the manifolds boundary. 
We call this simplicial complex the \emph{boundary complex}. It has dimension $n-1$. 
% We see that the family of boundary faces constitute a simplicial complex, which we call \textit{boundary complex}.
% Any point on the boundary lies within some boundary simplex, and hence the boundary complex is a triangulation of the boundary. 
% Definitions imply that the boundary complex is a manifold triangulation of dimension $n-1$.
% The boundary simplices of a manifold triangulation of dimension $n$ constitute a manifold triangulation themselves, of dimension $n-1$, which triangulate the boundary of the underlying space. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\\

We continue with a few more observations about manifold triangulations.

\begin{lemma}\label{lemma:startopology}
    Let $\calT$ be a finite $n$-dimensional simplicial complex whose underlying space is a manifold $\calM$. 
    \begin{itemize}
        \item If $S$ is an inner simplex, then $\patch_{\calT}(S)$ is a simplicial $n$-ball with $S$ as an inner simplex
        and $\carapace_{\calT}(S)$ is a simplicial $(n-1)$-sphere. 
        \item If $S$ is a boundary subsimplex, then $\patch_{\calT}(S)$ is a simplicial $n$-ball with $S$ as a boundary simplex,
        and $\carapace_{\calT}(S)$ is a simplicial $(n-1)$-ball.
        \item If the underlying space of $\calT$ is connected, then $\calT$ is strongly connected.
    \end{itemize}
\end{lemma}
\begin{proof}
    We prove these statements in several steps.
    \begin{enumerate}
    \item 
    Let $S$ be any simplex with vertices $v_0, v_1, \dots, v_k$, with midpoint $z_F$, and dimension $k$.
    Let $\calS := \patch_{\calT}(S)$ be its star. 
    Each $l$-dimensional simplex $T \in \calS$ that contains $S$ 
    has vertices $v_0, v_1, \dots, v_k, v_{k+1}^{S}, \dots, v_{l}^{S}$. 
    For any such simplex, we introduce a decomposition $T_{0}, \dots, T_{k}$, where each $T_{i}$ has vertices 
    \begin{align*}
        v_0, \dots, v_{i-1}, z_F, v_{i+1}, \dots, v_k, v_{k+1}^{S}, \dots, v_{l}^{S}.
    \end{align*}
    The collection $\calS'$ of these simplices and their subsimplices constitute a simplicial complex 
    that triangulates the same underlying set as $\calS$.
    Moreover, $\calS' = \patch_{\calS'}(z_F)$. 
    In particular, $z_F$ is a boundary vertex of $\calS'$ if and only if $S$ is a boundary simplex of $\calS$.

    So it remains to study the topology of vertex stars. Suppose that $S = \{z\}$ is a singleton simplex. 
    For $\delta > 0$ small enough, 
    \begin{align*}
        B_{\delta}(z) = \left\{ x \in \calM \suchthat d(x,z) \leq \delta \right\},
        \quad 
        S_{\delta}(z) = \left\{ x \in \calM \suchthat d(x,z) = \delta \right\},
    \end{align*}
    are subsets of $\patch_{\calT}(S)$.
    For each $K \in \patch_{\calT}(S)$ that contains $S$ and which has the complementary simplex $F_S$, 
    we easily find homeomorphisms $\phi_{K} : B_{\delta}(z) \cap K \rightarrow K$
    such that 
    $\phi_{K|S}$ is the identity,
    such that 
    $\phi_{K}(S_F) = S_{\delta}(z)$,
    and such that 
    for all $K, K' \in \calT$ with $K' \subseteq K$ we have $\phi_{K|K'} = \phi_{K'}$.

    If $z$ is an inner vertex of $\calS'$, 
    then the boundary simplices of $\calS'$,
    which are the boundary simplices of $\calS$, triangulate a topological sphere of dimension $n-1$.

    If $z$ is a boundary vertex of $\calS'$,
    which is the case if and only if $S$ is a boundary simplex, 
    then the underlying space of $\carapace(S)$ is homeomorphic to $S_{\delta}(z)$, 
    which is a topological ball of dimension $n-1$. % TODO: explain why

@@

Suppose that $\calT$ is an $n$-dimensional simplicial complex and we have an enumeration of the $n$-simplices $T_{0}, T_{1}, T_{2}, \dots \in \subsimplex_{n}(\calT)$.
For any enumeration, we call 
\[
    I_m 
    := 
    \big( 
        T_{0} \cup T_{1} \cup \dots \cup T_{m} 
    \big) 
    \cap 
    T_{m+1}
\]
be the $m$-th \textit{interface set}. 
% Note that this intersection is automatically a subcomplex of the boundary complex of the last simplex $T_{m}$.
We call the enumeration a \emph{shelling} if each interface $I_m$ is a manifold of dimension $n-1$.

\begin{remark}
    We interpret a shelling as the construction of a triangulation 
    by successively attaching simplices such that the intermediate triangulations are well-behaved. 
    Conversely, the reverse enumeration describes a successive decomposition of the triangulation, hence the name ``shelling''.
\end{remark}
\begin{remark}
    Whether a simplicial complex is shellable can be checked, in principle, simply by trying out all the possibly enumerations.
    That we cannot do much better than this is captured in the result that testing for shellability is NP-complete~\cite{goaoc2019shellability}:
    this complexity result is even true if we merely consider simplicial complexes of dimension two embedded in some Euclidean space.
\end{remark}

We collect important examples of shellable triangulations.
Our main interest are local patches or stars within triangulations.

\begin{example}
    Any simplex $T$ trivially has a shelling. The boundary complex $\partial \calT(T)$ has a shelling:
    in fact, any enumeration of the boundary faces of $T$ constitutes a shelling.
\end{example}
\begin{example}
    The standard triangulation of the $n$-dimensional cube, the Kuhn triangulation, is shellable. 
    % https://scholar.google.de/scholar?hl=de&as_sdt=0%2C5&q=kuhn+triangulation+shelling&btnG=
\end{example}

\begin{lemma}    
    Any simplicial $2$-disk is shellable.
    Any simplicial $2$-sphere is shellable. 
\end{lemma}
\begin{proof}
    Let $\calT$ be a simplicial $2$-disk. 
    If $\calT$ contains only one triangle, then there is nothing to show. 
    Otherwise, there exists at least one triangle $T$ that touches the boundary of the disk at either one or two edges 
    {\color{red}Needs proof}. 
    Letting $\calT'$ be the triangulation obtained by removing $T$,
    we have another triangulation of the $2$-disk that intersects $T$ only at either two or one edges.
    Repeating this procedure yields an enumeration of the triangles of $\calT$,
    whose reverse is a shelling.

@@

\begin{example}
    Not all trianguable sets admit a triangulation that is also shellable. 
    Moreover, even if a set admits a shellable triangulation, not all of its triangulations might be shellable. 
    We refer to~\cite[Example 8.9]{ziegler2012lectures} for an examples of non-shellable triangulations of cubes and tetrahedra in three dimensions. 
\end{example}
\begin{remark}
    Patches around boundary simplices are not necessarily shellable when the dimension exceeds $3$.
    For example, there exists a non-shellable triangulation of a tetrahedron. 
    If we extend this triangulation to a triangulation of a hypertetrahedron by suspending it from a new point $v_\star$, 
    then the resulting new triangulation is non-shellable and coincides with the patch around $v_\star$.
\end{remark}

@@

\begin{lemma}    
    If an $n$-dimensional simplicial complex $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots$ and is non-branching, then it triangulates a manifold, possibly with boundary.
    In particular, $T_{0} \cup T_{1} \cup \dots \cup T_{m}$ is a manifold with boundary for all $m \geq 0$.
\end{lemma}
\begin{proof}    
\end{proof}

% The notion of shelling is taken from Ziegler's book~\cite{ziegler2012lectures}

@@

% Square 
% L-shaped 
% Slit
% Cube 
% Fichera
% Crossed bricks
